## Sampling from the Binomial Distribution

We can use the **rbinom** command to do so. The general notation for a binomial/Bernouli distribution is: $X\sim B(n,P)$\
where $n$ is the number of identical trials, or sample size, and $P$ is the specified probability.\
\
The **rbinom** command uses the following format:/ rbinom(n = *Total size*, size = *Sample Size*, prop = *Probability*).

```{r}
# N = 1000
# X ~ B(15,1/3)
# Initialize rbinom:
y <- rbinom(n = 1000, size = 15, prob = 1/3)

# Plot rbinom:
hist(x = y, freq = FALSE,
     xlab = 'Value',
     ylab = 'Relative Frequency',
     main = 'Relative Frequenct Histogram of Binomial Random Variable')
```

## Calculating Probabilities of Values of Binomial Variables

To find $P(Y = y_0) = P(y_0)$, we can use the *dbinom* command./
To find $P(Y\leq y_0)$, we can use the *pbinom* command.
```{r}
# Example 3.9 (1)
# Prob = 0.05
# n = 20
# P(Y <= 3) (At most 3)
pbinom(q = 3, size = 20, prob = 0.05)
```

```{r}
# Example 3.9 (2)
# Prob = 0.05
# n = 3
# P(Y = 3)
dbinom(x = 3, size = 20, prob = 0.05)
```




